Thermodynamic fragments for magic states in quantum computation

### 2021-04-13 magic_paper.tex
Fixing elements of stablizer proof.

In this section, we apply majorization to magic state distillation within a simple fragment, namely the unital fragment. This encompasses distillation protocols where one is restricted to \emph{unital operations}, meaning that $\E(\I/d) = \I/d$ for all free $\E$. This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}. To make things concrete, we shall consider qutrit magic states ($d=3$) as qutrit systems don't exhibit the subtleties and peculirities of qubit systems, while they admit non-trivial structure (e.g. Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.

@@

These bounds can be interpreted in two different ways: 
\begin{enumerate}
\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
\item The state $\sigma$ can also reflect actual hardware limitations or some kind of biased noise model in which $\sigma$ is an equilibrium state.
\end{enumerate}
Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$. Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, expressed as
\begin{equation}
	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
\end{equation}
Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$. Again, under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the thermodynamic free energy of the equilibrium state.

@@

\begin{theorem}\label{thm:stab_bounds}
	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state. 
We define $\beta_\star = 1/kT_\star$ through the relation
\begin{equation}
	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
\end{equation}
where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$. \nick{is the ``overlap'' statement precise enough?} For $\beta \leq \beta_\star$, we define a threshold noise level
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
\end{equation}
Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
\end{equation}
Otherwise if $\beta > \beta_{\star}$,
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
\end{equation}
In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
\end{theorem}
A few comments can be given on this result. 
Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
This is apparent by simple numerical calculations on the entirety of the curves.
Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
Given that we work with qutrits this seems surprising, but does deserve further study.

@@

Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
The stabilizer state $\sigma$ can now be written as 
\begin{equation}
	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
\end{equation}
where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis. Let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$. Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary. Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$. However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space. We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.

The Wigner distribution of state $\sigma$ is then given by
\begin{align}
	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_{x}}}{3\Z_\beta},
\end{align}
where $x$ labels one of the three vertical lines in the phase space.
Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined. States that are not full-rank can be addressed as a limiting case of the above.

The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
\begin{equation}
	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_{\rm{S}}}}{\W[\bmx]{\sigma}},
\end{equation}
which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split_thermal}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different rescaled values.}
    The rescaled distribution attains a unique value in each of the four regions is proportional to the value depicted in the region, according to~\cref{eq:bmw_rescaled}.
    }
    \label{fig:pd_split_thermal}
\end{figure}

@@

In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
We can also assume that $n$ is even, so that we need the sum $\alpha = i+j+k$ to be even for the expression to be positive.

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. 
To determine this transition we set
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)} \coloneqq \frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.
If $E_{\rm{max}} = E_0$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. 
Otherwise, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2.
\end{equation}
Below the threshold, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
\end{equation}
This encompasses the case $E_{\rm{max}} = E_0$.
For $\beta > \beta_\star$, we have
\begin{equation*}
	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_s)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
\end{equation*}
so there is no transition and we set $\epsilon_\star = 0$.

The maximum component can then be expressed as
\begin{equation}
w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
	\end{cases}
\end{equation}
so the multiplicity in each case is $3^n$.

Using the appropriate indices in~\cref{eq:ncopy_wrho,eq:ncopy_wsigma}, the first elbow coordinates can now be expressed as
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}
The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we have three scenarios of relevance to magic distillation:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
\end{enumerate}
The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon$, which would imply that the output magic state is noisier than the input state.

>>>>

In this section, we apply majorization to magic state distillation within a simple fragment, namely the unital fragment. This encompasses distillation protocols where one is restricted to \emph{unital operations}, meaning that $\E(\I/d) = \I/d$ for all free $\E$. This is a particularly powerful set of operations, which for example include all Weyl-covariant channels~\cite{cit:gross3}. To make things concrete, we shall consider qutrit magic states ($d=3$) as the Wigner representation is simpler than $d=2$, while they admit non-trivial structure (e.g. Hamiltonians with two different energy gaps) and still are sufficiently simple to analyse in detail.

@@

These bounds can be interpreted in two different ways: 
\begin{enumerate}
\item As a family of upper bounds parameterised by an abstract stabiliser state $\sigma$.
\item The invariant state $\sigma$ reflects actual hardware limitations, a biased noise model, or a statement of the ambient thermal environment for the system.
\end{enumerate}
In what follows we shall be agnostic about which of the two apply. Without loss of generality, we can always write a full-rank stabiliser state $\sigma$ in the form $\sigma =  \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and effective Hamiltonian $H$. Our results will also depend on the free energy $F(\beta)$ of the state $\sigma$, expressed as
\begin{equation}
	F(\beta) \coloneqq \tr[H \sigma] - \beta^{-1}S(\sigma) = -\beta^{-1}\log{\Z_\beta}.
\end{equation}
Here $S(\sigma)$ is the von Neumann entropy $S(\sigma) \coloneqq -\tr[\sigma\log{\sigma}]$. Note that under interpretation (1) above, this is an abstract entropic measure of the stabilizer state, while, under interpretation (2), it corresponds to the actual thermodynamic free energy of the equilibrium state.

@@

\begin{theorem}\label{thm:stab_bounds}
	Given a theory of magic $\R = (\F, \O)$, let $\sigma$ be any qutrit stabiliser state, and write the state as $\sigma = \frac{1}{\Z} e^{-\beta H}$, where $H$ has eigenvalues $E_0, E_1, E_2$, and $\beta$ is an effective inverse temperature for the state. 
We define $\beta_\star = 1/kT_\star$ through the relation
\begin{equation}
	E_{\rm max} - E_s \eqqcolon kT_\star \ln 2,
\end{equation}
where $E_{\rm max} = \max\{E_0, E_1, E_2\}$ and $E_s$ is the eigenvalue of the eigenstate that overlaps the negative component of $\rho_S(\epsilon)$ in the Wigner representation. For $\beta \leq \beta_\star$, we define a threshold noise level
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm max} - E_s)\beta}}.
\end{equation}
Then, any distillation rate $R(\epsilon, \beta)$ in the $\sigma$--fragment of a magic theory is bounded as follows:\\
If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_s - F(\beta))}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_{\rm max} - E_s)(\beta_{\star} - \beta)}{\beta (E_s - F(\beta))}.
\end{equation}
Otherwise if $\beta > \beta_{\star}$,
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_{\rm max} - F(\beta))}.
\end{equation}
In the above expressions $F(\beta)$ is the effective free energy of the stabilizer state.
\end{theorem}
A few comments can be given on this result. 
Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. 
Secondly, these bounds are derived based on analysis of only a part of the Lorenz curves and can be improved via a finer analysis. 
This is apparent by simple numerical calculations on the entirety of the curves.
Specifically, the existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure. 
Finally, it is notable that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_{\rm max} - E_s$, where $kT_\star = \beta_\star^{-1}$. 
It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. 
Given that we work with qutrits this seems surprising, but does deserve further study.

@@

Let $\displaystyle \sigma = e^{-\beta H} / \Z_\beta$ be a stabiliser state, where $\beta \geq 0$ and $H = E_0 \ketbra{\varphi_0} + E_1 \ketbra{\varphi_1} + E_2 \ketbra{\varphi_2}$ is an eigendecomposition of $H$.
The stabilizer state $\sigma$ can now be written as 
\begin{equation}
	\sigma = \frac{e^{-\beta E_0}}{\Z_\beta} \ketbra{\varphi_0} + \frac{e^{-\beta E_1}}{\Z_\beta} \ketbra{\varphi_1} + \frac{e^{-\beta E_2}}{\Z_\beta} \ketbra{\varphi_2},
\end{equation}
where $\{\ket{\varphi_k}\<\varphi_k|\}$ are pure, orthonormal stabiliser states, which can be represented in terms of generalized Paulis. To make our analysis simpler we perform a change of basis that does not affect the Wigner negativity of the problem. We let $C$ be the unitary transforming each $|\varphi_k\>\<\varphi_k|$ to $|k\>\<k|$. Since the Clifford group is the normalizer of the Heisenberg-Weyl group this implies that $C$ is a Clifford unitary. Therefore, $C$ maps $\sigma$ to another stabilizer state that is diagonal in the computational basis, and we can therefore assume without loss of generality that $\sigma$ is diagonal in $\{|0\>,|1\>, |2\>\}$. However, this choice means that the location of the negative Wigner component $-v(\epsilon)$ of the strange state will be transformed on the discrete phase space. We denote by $E_s$ the eigenvalue of $H$ where the associated eigenvector has Wigner distribution overlapping the negative component of the magic state $C\rho_S(\epsilon)C^\dagger$.  This is unique, since the eigenstates form an orthonormal basis.

The Wigner distribution of state $\sigma$ is then given by
\begin{align}
	\W[\bmx]{\sigma} &= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta}W_{\ketbra{k}}(x, p) \nonumber\\
	&= \sum\limits_{k=0}^2 \frac{e^{-\beta E_k}}{\Z_\beta} \delta_{x, k} = \frac{e^{-\beta E_x}}{3\Z_\beta},
\end{align}
where $x$ labels one of the three vertical lines in the phase space.
Since we have restricted to full-rank states, all Wigner components are strictly positive, and so the pre-order $\prec_{\sigma}$ is well-defined. States that are not full-rank can be addressed as a limiting case of the above.

The Strange state rescaled distribution for a magic state $\rho_S(\epsilon)$ is now given by 
\begin{equation}
	\widetilde{\rm{W}}_{\rho_{\rm{S}}|\sigma}(\bmx) = \frac{\W[\bmx]{\rho_S}}{\W[\bmx]{\sigma}},
\end{equation}
which attains four distinct values on the phase space, naturally splitting it into four regions as illustrated in the~\cref{fig:pd_split_thermal}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.45]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions for $W_{\rho | \sigma}(\x)$.}
    Here the negative component of the magic state overlaps the Wigner distribution of $|0\>$. The rescaled distribution attains a single value in each of the four regions that is proportional to the value depicted in the region, see~\cref{eq:bmw_rescaled}.
    }
    \label{fig:pd_split_thermal}
\end{figure}

@@

In order to construct the $n$--copy Lorenz curve $\lc{\rho_{\rm{S}}^{\otimes n}}{\sigma^{\otimes n}}$ we need to order the components of the distribution, $w(\rho_{\rm{S}} | \sigma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the maximum component,
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} \coloneqq (3\Z)^{n}\times \nonumber\\
	&\max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_s} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:max_slope}
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
However, for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$, and so since we assume that $n$ is even we need that the sum $\alpha = i+j+k$ to be even for the expression to be positive.

Given an even value for $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_s}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&w(\rho_{\rm{S}} | \sigma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_s}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_s)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_s)}$ is less than $1$ then the maximum occurs at $\alpha=0$, otherwise it occurs at $\alpha = n$. For a fixed stabilizer state $\sigma$ this transition is determined by the value of the depolarising noise parameter $\epsilon$ of the noisy magic state. This transition occurs at $\epsilon = \epsilon_\star$ where
\begin{equation}\label{eq:noise_transition}
	\frac{u(\epsilon_\star)}{v(\epsilon_\star)} e^{\beta (E_{\rm{max}} - E_s)} = \frac{3-\epsilon_\star}{6-8\epsilon_\star} e^{\beta (E_{\rm{max}} - E_s)} = 1.
\end{equation}
If $E_{\rm{max}} = E_s$, namely if the state negativity lies in the same phase space region as the highest energy, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$. However, the condition that $\epsilon_\star \ge 0$ also implies a constraint on the effective temperature of the stabilizer state. Specifically, there is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_s} \ln2,
\end{equation}
such that for the regime $0 \leq \beta \leq \beta_\star$ a transition noise level $\epsilon_\star$ exists, and for $\beta > \beta_\star$ no such transition exists. The transition value for the noise is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_s)\beta}}.
\end{equation}
The quantity $w(\rho_{\rm{S}} | \sigma)_{\rm{max}}$ is now given by
\begin{equation*}
w(\rho_{\rm{S}} | \sigma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_s}, &\mbox{if }\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\mbox{if }\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation*}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, so the multiplicity is $m_{000} = 1$, while
Case $\rm{(C2)}$ corresponds to
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2,
	\end{cases}
\end{equation}
so the multiplicity in each case is $3^n$.

Using that $F(\beta) = -\beta^{-1} \log \Z$, the first elbow coordinates in the two cases are now given by
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left(\frac{1}{3^n} e^{-n\beta (E_s - F(\beta))}, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( e^{-n\beta (E_{\rm{max}}-F(\beta))}, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}
\ddd{[Are the factors of 3 correct in the previous equation?]} To obtain the distillation bounds from majorization we can now compute the above terms for both the input and output states. Depending on the noise parameters $\epsilon, \epsilon'$ for the initial and target states the Lorenz curve data may fall into either case $\rm{(C1)}$ or case $\rm{(C2)}$.
Specifically, we have three scenarios of relevance to magic distillation:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_s$ or $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_s$, $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $E_{\rm{max}} > E_s$, $\beta \geq \beta_{\star}$.
\end{enumerate}
The fourth case $\rm{(C1)} \rightarrow \rm{(C2)}$ is not considered as it would correspond to $\epsilon \leq \epsilon_\star < \epsilon'$, which would imply that the output magic state is noisier than the input state.
